---
title: "UNESCO World Heritage Sites 2019"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: spacelab
---

```{r setup, include=FALSE}
library(flexdashboard)
```
```{r warning=FALSE,message=FALSE}
library(lubridate)
library(scales)
library(readr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyr)
library(glue)
library(viridis)
library(leaflet)
library(treemapify)
library(skimr)
library(DT)
library(reshape2)
```

```{r warning=FALSE,message=FALSE}
wh <-
  read_csv("C:/SyabaruddinFolder/Work/Algoritma/DATAVIZcourse/InteractivePlot/LBB/wh.csv")

whc <- wh %>%
  mutate(
    category = as.factor(category),
    country = as.factor(states_name_en),
    region = as.factor(region_en),
    date_recorded = year(as.Date(as.character(date_inscribed), format = "%Y")),
    name = name_en,
    danger = as.factor(danger)
  ) %>%
  select(category,
         country,
         region,
         name,
         date_recorded,
         danger,
         longitude,
         latitude) %>%
  filter(
    region == "Europe and North America" |
      region == "Asia and the Pacific" |
      region == "Latin America and the Caribbean" |
      region == "Africa" |
      region == "Arab States"
  )


```





Global   {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Category Globally

```{r}
whcat <- whc %>%
  group_by(category) %>%
  summarise(freq = n())  %>%
  mutate(label = glue("Category: {category}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(category, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whcat, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = whc$longitude,
  lat = whc$latitude,
  popup = whc$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic
)

map
```

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Region Globally

```{r}
whreg <- whc %>%
  group_by(region) %>%
  summarise(freq = n()) %>%
  mutate(label = glue("Region: {region}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(region, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = region), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whreg, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Registered by Year

```{r}
whdate <- whc %>%
  group_by(date_recorded,region) %>% 
  summarise(freq=n()) %>% 
  mutate(label=glue(
    "Year Recorded: {date_recorded}
     Region: {region}
     Number of Sites: {freq}"
  )) %>% 
  ggplot(aes(x=date_recorded,y=freq,text=label,col=region,group=1))+
  geom_line() + geom_point() +
  labs(title="",
       x="Registration Year",
       y="Number of Sites") +
  theme_bw()

ggplotly(whdate,tooltip = "text") %>% layout(legend = list(
  orientation = "h",
  x = 0,
  y = -0.3
))
```


Asia & The Pacific  {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Asia and the Pacific Region Countries

```{r}
whas <- whc %>%
  filter(region=="Asia and the Pacific") %>% 
  group_by(country) %>%
  summarise(freq = n()) %>%
  mutate(label = glue(
    "Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = country), show.legend = F) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whas, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map Asia and The Pacific Region

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

whasia <-whc %>%
  filter(region=="Asia and the Pacific")

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = whasia$longitude,
  lat = whasia$latitude,
  popup = whasia$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic,
  label = whasia$name,
  
)
 

map
```

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Category in Asia and the Pacific Region

```{r}
whapac <- whc %>%
  filter(region=="Asia and the Pacific") %>% 
  group_by(category,country) %>%
  summarise(freq = n())  %>%
  mutate(label = glue(
    "Category: {category}
     Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  facet_grid(~category)+
  theme_bw() +
  
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whapac, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Danger Status in Asia and the Pacific Region

```{r}
whasiapac <- whc %>% 
  filter(region=="Asia and the Pacific") %>% 
  group_by(danger,country) %>% 
  summarise(freq=n())  %>% 
  mutate(label=glue(
    "Status: {danger}
     1 = Danger
     0 = Reserved
     Country : {country}
     Number of sites: {freq}
     "
  )) %>% 
  ggplot(aes(y=reorder(country,freq),x=freq, text=label)) + 
  geom_col(aes(fill=danger)) +
  facet_grid(~danger)+

  theme_bw()+
  labs(title = "",
       y= "",
       x= "Number of Sites")

ggplotly(whasiapac,tooltip = "text") %>% layout(showlegend=F)
```

Europe & North America  {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Europe and North America Region Countries

```{r}
whe <- whc %>%
  filter(region=="Europe and North America") %>% 
  group_by(country) %>%
  summarise(freq = n()) %>%
  filter(freq>5) %>% 
  mutate(label = glue(
    "Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = country), show.legend = F) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whe, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map Europe and North America Region 

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

wheu <-whc %>%
  filter(region=="Europe and North America")

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = wheu$longitude,
  lat = wheu$latitude,
  popup = wheu$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic
)

map
```


Column {data-width=500}
-----------------------------------------------------------------------


### World Heritage Sites by Category in Europe and North America Region

```{r}
wheuro <- whc %>%
  filter(region=="Europe and North America") %>% 
  group_by(category,country) %>%
  summarise(freq = n())  %>%
  filter(freq>3) %>% 
  mutate(label = glue(
    "Category: {category}
     Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  facet_grid(~category)+
  theme_bw() +
  
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(wheuro, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Danger Status in Europe and North America Region

```{r}
wheurope <- whc %>% 
  filter(region=="Europe and North America") %>% 
  group_by(danger,country) %>% 
  summarise(freq=n())  %>% 
  filter(freq>1) %>% 
  mutate(label=glue(
    "Status: {danger}
     1 = Danger 
     0 = Reserved
     Country : {country}
     Number of sites: {freq}
     "
  )) %>% 
  ggplot(aes(y=reorder(country,freq),x=freq, text=label)) + 
  geom_col(aes(fill=danger)) +
  facet_grid(~danger)+

  theme_bw()+
  labs(title = "",
       y= "",
       x= "Number of Sites")

ggplotly(wheurope,tooltip = "text") %>% layout(showlegend=F)
```

Latin America & The Caribbean  {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Latin America and the Caribbean Region Countries

```{r}
whlat <- whc %>%
  filter(region=="Latin America and the Caribbean") %>% 
  group_by(country) %>%
  summarise(freq = n()) %>%
  mutate(label = glue(
    "Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = country), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whlat, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map Latin America and the Caribbean Region 

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

whlatin <-whc %>%
  filter(region=="Latin America and the Caribbean")

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = whlatin$longitude,
  lat = whlatin$latitude,
  popup = whlatin$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic
)

map
```

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Category in Latin America and the Caribbean Region

```{r}
whlcat <- whc %>%
  filter(region=="Latin America and the Caribbean") %>% 
  group_by(category,country) %>%
  summarise(freq = n())  %>%
  mutate(label = glue(
    "Category: {category}
     Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  facet_grid(~category)+
  theme_bw() +
  
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whlcat, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Danger Status in Latin America and the Caribbean Region

```{r}
whdanglat <- whc %>% 
  filter(region=="Latin America and the Caribbean") %>% 
  group_by(danger,country) %>% 
  summarise(freq=n())  %>% 
  mutate(label=glue(
    "Status: {danger}
     1 = Danger
     0 = Reserved
     Country : {country}
     Number of sites: {freq}
     "
  )) %>% 
  ggplot(aes(y=reorder(country,freq),x=freq, text=label)) + 
  geom_col(aes(fill=danger)) +
  facet_grid(~danger)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(title = "",
       y= "",
       x= "Number of Sites")

ggplotly(whdanglat,tooltip = "text") %>% layout(showlegend=F)
```

Africa  {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Africa Region Countries

```{r}
whregaf <- whc %>%
  filter(region=="Africa") %>% 
  group_by(country) %>%
  summarise(freq = n()) %>%
  mutate(label = glue(
    "Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = country), show.legend = F) +
  theme_bw() +
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whregaf, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map Africa Region 

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

wharafrica <-whc %>%
  filter(region=="Africa")

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = wharafrica$longitude,
  lat = wharafrica$latitude,
  popup = wharafrica$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic
)

map
```

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Category in Africa Region

```{r}
wharcat <- whc %>%
  filter(region=="Africa") %>% 
  group_by(category,country) %>%
  summarise(freq = n())  %>%
  mutate(label = glue(
    "Category: {category}
     Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  facet_grid(~category)+
  theme_bw() +
  
  labs(title = "World Heritage Sites by Category in Africa Region",
       x = "Number of Sites",
       y = "")


ggplotly(wharcat, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Danger Status in Africa Region

```{r}
whdangarab <- whc %>% 
  filter(region=="Africa") %>% 
  group_by(danger,country) %>% 
  summarise(freq=n())  %>% 
  mutate(label=glue(
    "Status: {danger}
     1 = Danger
     0 = Reserved
     Country : {country}
     Number of sites: {freq}
     "
  )) %>% 
  ggplot(aes(y=reorder(country,freq),x=freq, text=label)) + 
  geom_col(aes(fill=danger)) +
  facet_grid(~danger)+

  theme_bw()+
  labs(title = "",
       y= "",
       x= "Number of Sites")

ggplotly(whdangarab,tooltip = "text") %>% layout(showlegend=F)
```

Arab States  {data-icon="fa-globe-americas"}
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Arab Region Countries

```{r}
whregar <- whc %>%
  filter(region=="Arab States") %>% 
  group_by(country) %>%
  summarise(freq = n()) %>%
  mutate(label = glue(
    "Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = country), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw() +
  labs(title = "World Heritage Sites by Arab Region Countries",
       x = "Number of Sites",
       y = "")


ggplotly(whregar, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Distribution Map Arab Region 

```{r}
Pic <- makeIcon(
  iconUrl = "images (1).png",
  iconWidth = 100 * 0.35,
  iconHeight = 100 * 0.35
)

wharab <-whc %>%
  filter(region=="Arab States")

map <- leaflet()
map <- addTiles(map)

map <- addMarkers(
  map,
  lng = wharab$longitude,
  lat = wharab$latitude,
  popup = wharab$name,
  clusterOptions = markerClusterOptions(),
  icon = Pic
)

map
```

Column {data-width=500}
-----------------------------------------------------------------------

### World Heritage Sites by Category in Arab Region

```{r}
whar <- whc %>%
  filter(region=="Arab States") %>% 
  group_by(category,country) %>%
  summarise(freq = n())  %>%
  mutate(label = glue(
    "Category: {category}
     Country: {country}
     Number of sites: {freq}")) %>%
  ggplot(aes(
    y = reorder(country, freq),
    x = freq,
    text = label
  )) +
  geom_col(aes(fill = category), show.legend = F) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  facet_grid(~category)+
  theme_bw() +
  
  labs(title = "",
       x = "Number of Sites",
       y = "")


ggplotly(whar, tooltip = "text") %>%  layout(showlegend = F)
```

### World Heritage Sites Danger Status in Arab Region

```{r}
whdangarab <- whc %>% 
  filter(region=="Arab States") %>% 
  group_by(danger,country) %>% 
  summarise(freq=n())  %>% 
  mutate(label=glue(
    "Status: {danger}
     1 = Danger
     0 = Reserved
     Country : {country}
     Number of sites: {freq}
     "
  )) %>% 
  ggplot(aes(y=reorder(country,freq),x=freq, text=label)) + 
  geom_col(aes(fill=danger)) +
  facet_grid(~danger)+
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_bw()+
  labs(title = "",
       y= "",
       x= "Number of Sites")

ggplotly(whdangarab,tooltip = "text") %>% layout(showlegend=F)
```


Data Table {data-icon="fa-table"}
=======================================================================

Column {data-width=1000}
-----------------------------------------------------------------------

```{r}
datatable(whc)

```

